Efficient ancestry and mutation simulation with msprime 1.0

### 2021-09-19 paper.tex
Rework paragraph addressing inequalities.

An important goal of the msprime development model is to maximise
accessibility for prospective users and contributors. However, it is important
to acknowledge that under-representation persists in population genetics,
especially in methodology and open-source software
development~\citep{trinkenreich2021women}. The authorship
of our paper reflects this with a skew towards men and affiliations in the USA
and Europe. We know the importance of creating and strengthening networks to
develop and maintain a diverse community of contributors, and we are committed
to fostering a supportive and collaborative environment that helps to address these
inequalities in our field.

>>>>

An important goal of \msprime's development model is to maximise
accessibility for prospective users and contributors, and
to encourage diversity in our community.
Gender inequality is a major problem across
the sciences~\citep{shannon2019gender}
and in open source software development~\citep{trinkenreich2021women}.
Within our field, the contribution of women to early computational methods
in population genetics was marginalised~\citep{dung2019illuminating},
and women continue to be under-represented
in computational biology~\citep{bonham2017women}.
The authorship of our paper reflects these trends,
with a skew towards men and affiliations in the USA
and Europe. We know the importance of creating and strengthening networks to
develop and maintain a diverse community of contributors, and we are committed
to fostering a supportive and collaborative environment that helps to address these
inequalities in our field.
